Toronto Homicides and Shootings (To be Changed)

### 2024-09-25 paper/paper.qmd
Added in ward profile table

## Additional Tables

>>>>

## Additional Tables 
```{r}
#| label: tbl-wardprofile
#| tbl-cap:  Average total income of households in 2020 across the 25 wards of Toronto.
#| echo: false
#| warning: false
#| message: false

# Creates table
cleaned_ward_data |>
  rename(
    "Ward Number" = ward_num,
    "Ward Name" = ward_name,
    "Average total income of households in 2020 ($)" = avg_income
  ) |>
  kable()
```
